THESIS TITLE

### 2023-08-07 subsections/theory/rhodotron/rhodotron.tex
statE raw data added

% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{A circular accelerator}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{A linear accelerator}
\end{figure}

@@

Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{SUPERFISH simulation of a coaxial cavity}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{CST simulation of a coaxial cavity}
\end{figure}

@@

\begin{description}
    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity.
    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.
    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity.
    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again.
\end{description}

This cycle can be repeated as long as real world constraints such as; placements and dimentions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
After desired amount of pass has been completed, the electrons exit the accelerator.

This process is explained further in the following figures where $T$ is the period of the electric field.
% TODO : ADD ACCELERATION PROCESS OF RHODOTRON FIGURES HERE
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
\end{figure}

>>>>

% TODO : ADD CIRCULAR AND LINEAR ACCELERATOR PICTURES HERE

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{../../../figures/to_be_added.png}
    \caption{A linear proton accelerator in KAHVELab}
\end{figure}

@@

Coaxial design of the cavity concentrates the electric field, while the magnetic field diminishes in the middle of the cylinders. 
Therefore the electrons are injected and accelerated in the plane of zero magnetic field where the electric field is strongest.
% TODO : ADD SUPERFISH AND CST SIMULATIONS OF A SIMPLE RHODOTRON CAVITY MAYBE?????

@@

\begin{description}
    \item[First acceleration] Electrons in the rhodotron cavity are accelerated by the electric field created between two coaxial cylinders, towards the inner cylinder when they are ejected into the cavity. See \fromfig{rhod_cycle_1}
    \item[Inner shielding] While inside the inner cylinder, the cylinder acts as a faraday cage and shields the electrons inside while the electric field is being reversed.See \fromfig{rhod_cycle_2}
    \item[Second acceleration] Once the electrons leave the inner cylinder, they accelerate towards the outer cylinder by the reversed electric field until they leave the cavity. See \fromfig{rhod_cycle_3}
    \item[Magnets] After leaving the cavity, an electromagnet placed in their path steers the electrons back into the cavity in which time the electric field changes the direction again. See \fromfig{rhod_cycle_4}
\end{description}

This cycle can be repeated as long as real world constraints such as; placements and dimensions of the electromagnets, power requirements due to increasing magnetic field in order for sharper turns, can be overcomed.
After desired amount of pass has been completed, the electrons exit the accelerator.

This process is explained further in the following figures where $T$ is the period of the electric field.
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod1.pdf}
    \caption{$[0, \frac{T}{4}]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_1}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod2.pdf}
    \caption{$[\frac{T}{4}, \frac{T}{2}]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_2}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod3.pdf}
    \caption{$[\frac{T}{2}, \frac{3T}{4}]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_3}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{../../../figures/illustrations/rhod4.pdf}
    \caption{$[\frac{3T}{4}, T]$ time frame of a rhodotron}
    \label{fig:rhod_cycle_4}
\end{figure}
